---
title: "Hawaii Planned Comparisons"
author: "David McCullough"
date: "3/5/2021"
output:
  word_document: default
  html_document: default
---
```{r Data & libs, echo=FALSE, include=FALSE}
library(MASS)
library(AER)
load("~/General/Hawaii Dashboard/Output.RData")
Mod_df <- app_df
Mod_df$Hawaiian <- factor(Mod_df$`Q2 Are you Native Hawaiian?`,ordered = FALSE)
Mod_df$Hawaiian <- relevel(Mod_df$Hawaiian,ref = "No")
Mod_df$Loc <- factor(Mod_df$`Q3 In which county do you reside?`,ordered = FALSE)
Mod_df$Loc <- relevel(Mod_df$Loc,ref = "Honolulu County")
```

## RQ1

Q6 COVID-19 restrictions:To what extent do the following factors limit your access to education programs?

```{r Q6, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 COVID-19 restrictions:To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6)

exp(-p2q6$coefficients["HawaiianYes"])

```

Q6 Distance and transportation:To what extent do the following factors limit your access to education programs?

```{r Q6.2, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 Distance and transportation:To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6.2 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6.2)

```

Q6 Lack of time or competing priorities:To what extent do the following factors limit your access to education programs?

```{r Q6.3, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 Lack of time or competing priorities:To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6.3 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6.3)

cat(paste("\n\nHawaiians are",round(exp(-p0$coefficients["HawaiianYes"]),2),"times more likely to answer favorably.\n\n"))
```

Q6 Program requirements (for example, application forms, time of day, required volunteer hours):To what extent do the following factors limit your access to education programs?

```{r Q6.4, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 Program requirements (for example, application forms, time of day, required volunteer hours):To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6.4 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6.4)

```

Q6 Programs don't meet my family's needs:To what extent do the following factors limit your access to education programs?

```{r Q6.5, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 Programs don't meet my family's needs:To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6.5 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6.5)

```

Q6 Tuition or program fees:To what extent do the following factors limit your access to education programs?

```{r Q6.6, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q6 Tuition or program fees:To what extent do the following factors limit your access to education programs?`,levels = c("To a great extent", "To a moderate extent", "To some extent", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q6.6 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q6.6)

```
Q7 How connected do you feel to a spiritual or religious community?

```{r Q7, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q7 How connected do you feel to a spiritual or religious community?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q7 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q7)

```

Q8 How connected do you feel to an ethnic or cultural community?

```{r Q8, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q8 How connected do you feel to an ethnic or cultural community?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q8 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q8)

```

Q9 How connected do you feel to the geographic community in which you live?

```{r Q9, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q9 How connected do you feel to the geographic community in which you live?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q9 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q9)

```

Q10 How connected do you feel to your neighbors (for example, visiting with them, asking them to watch your home, offering help to them when they ask)?

```{r Q10, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q10 How connected do you feel to your neighbors (for example, visiting with them, asking them to watch your home, offering help to them when they ask)?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2)

```

Q31 How often do you spend time learning about Native Hawaiian culture?

```{r Q31, echo=FALSE}

Mod_df$Current_Q <- factor(Mod_df$`Q31 How often do you spend time learning about Native Hawaiian culture?`,levels = c("Daily", "Weekly", "Monthly", "Once or twice a year", "Never"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2q31 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2q31)
```

## RQ1, part 2

Q4 Worked with others in the community to achieve a common goal (for example, fundraising for the local library):In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.1, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4 Worked with others in the community to achieve a common goal (for example, fundraising for the local library):In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.1 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.1, test = "Chisq")

```

Q4 Participated in an event to address a community issue:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4 Participated in an event to address a community issue:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.2 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.2, test = "Chisq")

```

Q4 Organized an event to address a community issue:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4 Organized an event to address a community issue:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.3 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.3, test = "Chisq")

```

Q4  Written a letter or submitted testimony about an issue that is important to you:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4  Written a letter or submitted testimony about an issue that is important to you:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.4 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.4, test = "Chisq")

```

Q4 Met with a local official about an issue that is important to you:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4 Met with a local official about an issue that is important to you:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.5 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.5, test = "Chisq")

```

Q4 Made donations to benefit the community:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)

```{r Q4.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q4 Made donations to benefit the community:In the last 12 months, which of the following community-building activities have you participated in virtually or in person? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q4.6 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q4.6, test = "Chisq")

```

Q12 With my family and friends:If leadership means serving others and improving your community, where do you act as a leader? (Select all that apply)

```{r Q12, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q12 With my family and friends:If leadership means serving others and improving your community, where do you act as a leader? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q12 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q12, test = "Chisq")
```

Q34 How often do you spend time contributing to the well-being of the Native Hawaiian community?

```{r Q34, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q34 How often do you spend time contributing to the well-being of the Native Hawaiian community?`,levels = c("Daily","Weekly","Monthly","A couple of times a year",   "Rarely","Never"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q34 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q34)

```

## RQ1, part 3

Q15 Do you believe in a "higher power" such as God (Ke Akua) or other deities (personal, family, or Hawaiian gods)?

```{r Q15, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q15 Do you believe in a "higher power" such as God (Ke Akua) or other deities (personal, family, or Hawaiian gods)?`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q15 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q15, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q15$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q16 How important is your belief in a "higher power" to your well-being?

```{r Q16, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q16 How important is your belief in a "higher power" to your well-being?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q16 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q16)

cat(paste("\n\nHawaiians are",round(exp(-p2Q16$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))

```

Q17 How important is the health of the aina (land) and kai (ocean) to your well-being?

```{r Q17, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q17 How important is the health of the aina (land) and kai (ocean) to your well-being?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q17 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q17)

cat(paste("\n\nHawaiians are",round(exp(-p2Q17$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))

```

Q 18 How important is your cultural heritage to your well-being?

```{r Q18, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q 18 How important is your cultural heritage to your well-being?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q18 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q18)

cat(paste("\n\nHawaiians are",round(exp(-p2Q18$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))

```

Q 18 How important is your cultural heritage to your well-being?

```{r Q19, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q19 How important are your 'ohana (family) relationships to your well-being?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q19 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q19)

cat(paste("\n\nHawaiians are",round(exp(-p2Q19$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))
```

## RQ1, part 4

Q29 How much do you care about Native Hawaiian issues such as self-determination, native land rights, and the revitalization of Hawaiian language?

```{r Q29, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q29 How much do you care about Native Hawaiian issues such as self-determination, native land rights, and the revitalization of Hawaiian language?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)


pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q29 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q29)

cat(paste("\n\nHawaiians are",round(exp(-p2Q29$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))
```

Q28 How important is it for future generations to speak Olelo Hawai'i (Hawaiian language)?

```{r Q28, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q28 How important is it for future generations to speak Olelo Hawai'i (Hawaiian language)?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)


pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q28 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q28)

cat(paste("\n\nHawaiians are",round(exp(-p2Q28$coefficients["HawaiianYes"]),2),"times as likely to indicate importance.\n\n"))
```

Q27 I am currently learning Olelo Hawai'i.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q27, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q27 I am currently learning Olelo Hawai'i.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q27 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q27, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q27$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q27 I am fluent in Olelo Hawai'i and continuously learning.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q27.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q27 I am fluent in Olelo Hawai'i and continuously learning.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q27.2 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q27.2, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q27.2$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q27 I am interested in learning Olelo Hawai'i, but cannot access learning resources due to cost, time, or other constraints.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q27.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q27 I am interested in learning Olelo Hawai'i, but cannot access learning resources due to cost, time, or other constraints.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q27.3 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q27.3, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q27.3$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q27 I am interested in learning Olelo Hawai'i, but don't know how to do so.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q27.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q27 I am interested in learning Olelo Hawai'i, but don't know how to do so.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q27.4 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q27.4, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q27.4$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q27 I am not interested in learning Olelo Hawai'i.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q27.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q27 I am not interested in learning Olelo Hawai'i.:Which of the following is true for you regarding learning Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q27.5 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q27.5, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(-p2q27.5$coefficients["HawaiianYes"]),2),"times less likely to answer \"yes\".\n\n"))
```

Q26 I can converse at a beginner level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can converse at a beginner level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q26$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q26 I can converse at an advanced level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can converse at an advanced level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26.2 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26.2, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p1$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q26 I can converse at an intermediate level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can converse at an intermediate level with other Olelo Hawai'i speakers.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26.3 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26.3, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p1$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q26 I can read Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can read Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26.4 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26.4, test = "Chisq")

cat(paste("\n\nHawaiians are",round(exp(p2q12$coefficients["HawaiianYes"]),2),"times more likely to answer \"yes\".\n\n"))
```

Q26 I can understand common words and phrases in Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can understand common words and phrases in Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26.5 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26.5, test = "Chisq")

```

Q26 I can write Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)

```{r Q26.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q26 I can write Olelo Hawai'i.:Which of the following is true for you regarding using Olelo Hawai'i (Hawaiian language)? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

pn <- glm(formula = Current_Q ~
             1,data = Mod_df,family = "binomial")

p0 <- glm(formula = Current_Q ~
         Hawaiian, data = Mod_df,family = "binomial")

p1 <- glm(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,family = "binomial")

p2q26.6 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(pn,p0,p1,p2q26.6, test = "Chisq")

```

## RQ1, part 5

Q35 How important are Native Hawaiian culture and values to solving the challenges facing Hawai'i today?

```{r Q35, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q35 How important are Native Hawaiian culture and values to solving the challenges facing Hawai'i today?`,levels = c("Extremely", "Quite a bit", "Moderately", "A little bit", "Not at all"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q35 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q35)

```

## RQ2, part 1

Q21 How satisfied are you with your overall quality of life

```{r Q21, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q21 How satisfied are you with your overall quality of life?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q21 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q21)

```

## RQ2, part 2

Q23 Overall, how hopeful are you about Hawai'i's future?

```{r Q23, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q23 Overall, how hopeful are you about Hawai'i's future?`,levels = c("Extremely hopeful",  "Very hopeful", "Pretty hopeful", "A little hopeful", "Not at all hopeful"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q23 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q23)

```

## RQ2, part 3

Q44 and 46 are word clouds

Q47 What is your highest level of education?

```{r Q47, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q47 What is your highest level of education?`,levels = c("Less than high school", "High school or equivalent", "Some college or Associate's degree", "Bachelor's degree", "Masters degree or higher"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q47 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q47)

```

## RQ2, part 4

Determine good analysis approach

## RQ2, part 5

Q40 Before the COVID-19 crisis, how would you have described your household's financial situation?

```{r Q40, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q40 Before the COVID-19 crisis, how would you have described your household's financial situation?`,levels = c("Enough savings to pay for more than 1 year of expenses", "Enough savings to pay for 3 months to 1 year of expenses", "Enough savings to pay for 1 to 2 months of expenses", "Living paycheck-to-paycheck (not saving any money)", "Not making ends meet (have to rely on loans or credit cards to pay bills)"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q40 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q40)

```

```{r Q41, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q41 During the COVID-19 crisis, how would you describe your household's financial situation?`,levels = c("Enough savings to pay for more than 1 year of expenses", "Enough savings to pay for 3 months to 1 year of expenses", "Enough savings to pay for 1 to 2 months of expenses", "Living paycheck-to-paycheck (not saving any money)", "Not making ends meet (have to rely on loans or credit cards to pay bills)"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q41 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q41)

```

## RQ3, part 1

Q37 When it comes to strengthening Native Hawaiian communities, which statement best represents you?

```{r Q37, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q37 When it comes to strengthening Native Hawaiian communities, which statement best represents you?`,levels = c("Strengthening Native Hawaiian communities is both a <strong>personal and professional</strong> goal.", "Strengthening Native Hawaiian communities is a <strong>personal</strong> goal.", "Strengthening Native Hawaiian communities is a <strong>professional </strong>goal.", "Strengthening Native Hawaiian communities is <strong>not a goal for me but it might be someday</strong>.", "Strengthening Native Hawaiian communities is <strong>not a goal</strong> for me."),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q37 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q37)

```

## RQ3, part 2

Q33 When making a difficult decision or taking on a challenging task, how often do you draw upon your cultural heritage?

```{r Q33, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q33 When making a difficult decision or taking on a challenging task, how often do you draw upon your cultural heritage?`,levels = c("Always", "Most of the time", "Sometimes", "Rarely", "Never"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q33 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q33)

```

## RQ3, part 3

See question 4 results

## RQ3, part 4

Q30 No:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.1, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 No:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.1 <- glm(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,family = "binomial")

anova(p2q30.1, test = "Chisq")

```

Q30 Yes, for cultural reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 Yes, for cultural reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.2 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q30.2, test = "Chisq")

```

Q30 Yes, for health reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 Yes, for health reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.3 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q30.3, test = "Chisq")

```

Q30 Yes, for recreational reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 Yes, for recreational reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.4 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q30.4, test = "Chisq")

```

Q30 Yes, for spiritual or religious reasons. :Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 Yes, for spiritual or religious reasons. :Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.5 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q30.5, test = "Chisq")

```

Q30 Yes, for subsistence reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)

```{r Q30.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q30 Yes, for subsistence reasons.:Do you interact with the aina (land) or kai (ocean) for cultural, spiritual, subsistence, health, or recreational reasons? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q30.6 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q30.6, test = "Chisq")

```

## RQ4, part 1

See output for Q17 and 19 above

## RQ4, part 2

Q39 Caregiving for children:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Caregiving for children:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39, test = "Chisq")

```

Q39 Caregiving for dependent adults:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Caregiving for dependent adults:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.2 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.2, test = "Chisq")

```

Q39 Getting laid off or being on unemployment:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Getting laid off or being on unemployment:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.3 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.3, test = "Chisq")

```

Q39 Health/getting sick:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Health/getting sick:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.4 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.4, test = "Chisq")

```

Q39 Losing health insurance:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Losing health insurance:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.5 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.5, test = "Chisq")

```

Q39 Loss of services in my community:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Loss of services in my community:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.6 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.6, test = "Chisq")

```

Q39 Loss of small businesses in my community:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.7, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Loss of small businesses in my community:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.7 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.7, test = "Chisq")

```

Q39 Mental and emotional well-being:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.8, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Mental and emotional well-being:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.8 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.8, test = "Chisq")

```

Q39 My children falling behind in school:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.9, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 My children falling behind in school:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.9 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.9, test = "Chisq")

```

Q39 Not being able to find work:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)

```{r Q39.10, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q39 Not being able to find work:What, if anything, are you worried about in light of the COVID-19 crisis for you or your family? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q39.10 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q39.10, test = "Chisq")

```

## RQ4, part 3

Q43 Members of my household depend on community spaces like libraries and public "hot spots" for internet access.:Which of the following is true for you regarding digital connectivity? (Select all that apply)

```{r Q43, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q43 Members of my household depend on community spaces like libraries and public "hot spots" for internet access.:Which of the following is true for you regarding digital connectivity? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q43 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q43, test = "Chisq")

```

Q43 My household has enough internet-capable devices for everyone to be online at the same time, if needed.:Which of the following is true for you regarding digital connectivity? (Select all that apply)

```{r Q43.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q43 My household has enough internet-capable devices for everyone to be online at the same time, if needed.:Which of the following is true for you regarding digital connectivity? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q43.2 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q43.2, test = "Chisq")

```

Q43 My household has internet access at a speed and quality that meets our needs.:Which of the following is true for you regarding digital connectivity? (Select all that apply)

```{r Q43.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q43 My household has internet access at a speed and quality that meets our needs.:Which of the following is true for you regarding digital connectivity? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q43.3 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q43.3, test = "Chisq")

```

Q43 My household plans to keep our internet subscription at the same level.:Which of the following is true for you regarding digital connectivity? (Select all that apply)

```{r Q43.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q43 My household plans to keep our internet subscription at the same level.:Which of the following is true for you regarding digital connectivity? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q43.4 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q43.4, test = "Chisq")

```

Q43 The internet-capable devices in my household are easy to use for essential purposes like school or work.:Which of the following is true for you regarding digital connectivity? (Select all that apply)

```{r Q43.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q43 The internet-capable devices in my household are easy to use for essential purposes like school or work.:Which of the following is true for you regarding digital connectivity? (Select all that apply)`,levels = c("No","Yes"),ordered = FALSE)

p2q43.5 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q43.5, test = "Chisq")

```

## RQ4, part 4

Q20 Connecting with the aina (land) or kai (ocean):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Connecting with the aina (land) or kai (ocean):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20, test = "Chisq")

```

Q20 Expressing myself through art, music, writing, dance, cooking, etc.:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Expressing myself through art, music, writing, dance, cooking, etc.:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.2 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.2, test = "Chisq")

```

Q20 Living a healthy lifestyle (for example, nutrition, exercise, support from health professionals, etc.):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Living a healthy lifestyle (for example, nutrition, exercise, support from health professionals, etc.):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.3 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.3, test = "Chisq")

```

Q20 Living a healthy lifestyle (for example, nutrition, exercise, support from health professionals, etc.):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Living a healthy lifestyle (for example, nutrition, exercise, support from health professionals, etc.):Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.4 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.4, test = "Chisq")

```

Q20 Prayer, meditation or mindfulness:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Prayer, meditation or mindfulness:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.5 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.5, test = "Chisq")

```

Q20 Setting daily goals, routines, or priorities:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Setting daily goals, routines, or priorities:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.6 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.6, test = "Chisq")

```

Q20 Stress reducing substances such as tobacco, alcohol, non-prescribed medications, etc.:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.7, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Stress reducing substances such as tobacco, alcohol, non-prescribed medications, etc.:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.7 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.7, test = "Chisq")

```

Q20 Support from 'ohana or friends:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)

```{r Q20.8, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q20 Support from 'ohana or friends:Which of the following strategies help you cope with loss or other difficult times? (Choose your top three)`,levels = c("No","Yes"),ordered = FALSE)

p2q20.8 <- glm(formula = Current_Q ~
         Hawaiian *
         Loc,data = Mod_df,family = "binomial")

anova(p2q20.8, test = "Chisq")

```

## RQ5, part 1

See output for Q4 above

## RQ5, part 2

See output for Q6 above

Q5 Charter schools:How satisfied are you with the quality of the following education programs in your community?
```{r Q5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Charter schools:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5)

```

Q5 Colleges, community colleges, and universities:How satisfied are you with the quality of the following education programs in your community?

```{r Q5.2, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Colleges, community colleges, and universities:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.2 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.2)

```

Q5 Native Hawaiian-focused education programs:How satisfied are you with the quality of the following education programs in your community

```{r Q5.3, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Native Hawaiian-focused education programs:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.3 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.3)

```

Q5 Out-of-school programs (for example, summer or intercession programs):How satisfied are you with the quality of the following education programs in your community?

```{r Q5.4, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Out-of-school programs (for example, summer or intercession programs):How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.4 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.4)

```

Q5 Preschools:How satisfied are you with the quality of the following education programs in your community?

```{r Q5.5, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Preschools:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.5 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.5)

```

Q5 Private K-12 schools:How satisfied are you with the quality of the following education programs in your community?

```{r Q5.6, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Private K-12 schools:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.6 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.6)

```

Q5 Public K-12 schools:How satisfied are you with the quality of the following education programs in your community?

```{r Q5.7, echo=FALSE}
Mod_df$Current_Q <- factor(Mod_df$`Q5 Public K-12 schools:How satisfied are you with the quality of the following education programs in your community?`,levels = c("Very satisfied","Satisfied","Neutral","Unsatisfied","Very unsatisfied"),ordered = TRUE)

pn <- polr(formula = Current_Q ~
             1,data = Mod_df,Hess=TRUE)

p0 <- polr(formula = Current_Q ~
         Hawaiian, data = Mod_df,Hess=TRUE)

p1 <- polr(formula = Current_Q ~
         Loc +
         Hawaiian,data = Mod_df,Hess=TRUE)

p2Q5.7 <- polr(formula = Current_Q ~
         Loc *
         Hawaiian,data = Mod_df,Hess=TRUE)

anova(pn,p0,p1,p2Q5.7)

```

## RQ5, part 3

See Q9 output above

## RQ5, part 4

See Q10 output above

## RQ5, part 5

See Q12 output above

## RQ5, part 6

See Q17 output above

## RQ5, part 7

See Q19 output above

## RQ5, part 8

See Q22 and 23 output above

## RQ5, part 9

See Q43 output above

## RQ5, part 9

See Q8 output above

## RQ5, part 9

See Q7 output above